### 2023-12-20 manuscript.tex
. [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/77b476d159419ad0a5a90137e64696ffcef93452.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/77b476d159419ad0a5a90137e64696ffcef93452/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/7279410024

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/8e184b39376fd1af83cf5293f0d3d52bc35102c9/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/8e184b39376fd1af83cf5293f0d3d52bc35102c9}{MMV-Lab/im2im-paper@8e184b3}
on December 20, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-vm45dW9e}{}}%
\CSLLeftMargin{54. }%
\CSLRightInline{\textbf{The hiPSC single-cell image dataset}
\CSLBlock{Jianxu Chen, Kimverly Metzler, Allen Institute Contributors} \url{https://open.quiltdata.com/b/allencell/packages/aics/hipsc_single_cell_image_dataset}}

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/77b476d159419ad0a5a90137e64696ffcef93452/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/77b476d159419ad0a5a90137e64696ffcef93452}{MMV-Lab/im2im-paper@77b476d}
on December 20, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-vm45dW9e}{}}%
\CSLLeftMargin{54. }%
\CSLRightInline{\textbf{The hiPSC single-cell image dataset}
\CSLBlock{Jianxu Chen, Kimberly Metzler, Allen Institute Contributors} \url{https://open.quiltdata.com/b/allencell/packages/aics/hipsc_single_cell_image_dataset}}
